Online {\IterComp}

### 2017-11-15 work.tex
Minor error

    Figure~\ref{fig:work-vs-O0time} shows the correlation coefficient between the work metric ($\Delta W$) and the runtime of the
    unoptimized version for 14 benchmarks that were not used for training the linear model. The work metric correlates very strongly with
    runtime for almost all the benchmarks, the correlation coefficient being typically higher than $0.98$. The exception is the benchmarks
    based on \texttt{tiff}. The coefficient for them ranges from $0.47$ to $0.96$. Despite that, in most cases work is an excellent proxy
    for unoptimized runtime. For the rest, our Section~\ref{sec:results} evaluation shows that our work metric is still useful for quantifying
    performance.

>>>>

    Figure~\ref{fig:motivation-speedups} shows the correlation coefficient between the work metric ($\Delta W$) and the runtime of the
    unoptimized version for 14 benchmarks that were not used for training the linear model. The work metric correlates very strongly with
    runtime for almost all the benchmarks, the correlation coefficient being typically higher than $0.98$. The exception is the benchmarks
    based on \texttt{tiff}. The coefficient for them ranges from $0.47$ to $0.96$. Despite that, in most cases work is an excellent proxy
    for unoptimized runtime. For the rest, our Section~\ref{sec:results} evaluation shows that our work metric is still useful for quantifying
    performance.
